Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-30 latex/appendix.tex
app

	\item [WIP]
		Sampling also matters in adversarial training for deep metric learning.

@@

	\item [WIP] 7-step PGD and better aligned comparison: compare when
		these methods reach similar retrieval performance.

@@

>>>>

\begin{itemize}

	\item [*]
		Sampling also matters in adversarial training for deep metric learning.

@@

	\item [*] 7-step PGD and better aligned comparison: compare when
		these methods reach similar retrieval performance.

@@

\end{itemize}
